### 2021-02-20 paper.tex
Rework tab section.

\subsection*{Tabs}
One major issue in working with SNIK Graph was the missing ability of organizing teaching scenarios.
For this subgraphs of the ontology have to be extracted and organized.
A feature of SNIK Graph, tabs, allows multi-instance usage.
We use the javascript framework GoldenLayout\footnote{\url{https://golden-layout.com/}} to build and load independent SNIK Graph instances into containers that can be organized around the browser window.
Besides the tabs menu these instances can be organized ie side-by-side.
This feature allows better workflows in preparation and presentation of teaching scenarios.
Additionally the design allows to store and restore sessions, that can be shared around computers and persons.
We use JSON formatted files for export and import.

>>>>

\subsection*{Tabs}
%For this subgraphs of the ontology have to be extracted and organized.
%A feature of SNIK Graph, tabs, allows multi-instance usage.
%One major issue in working with SNIK Graph was the missing ability of organizing teaching scenarios.
To organize teaching scenarios, independent SNIK Graph instances are loaded into containers\footnotemark{} that can be organized around the browser window.
\footnotetext{Implemented using the JavaScript GoldenLayout framework (\url{https://golden-layout.com/}).} 
These containers can either be accessed as tabs or freely partitioned.

%This feature allows better workflows in preparation and presentation of teaching scenarios.
%Additionally the design allows to store and restore sessions, that can be shared around computers and persons.
%We use JSON formatted files for export and import.
